---
title: "2022 Chippewa County Cover Crop Summary"
author: "Kolby Grint"
date: "2022-12-07"
output: html_document
---

```{r, echo= FALSE}
#loading packages
library(tidyverse)
library(readxl)
library(janitor)
library(unheadr)
library(ggplot2)
library(sf)
library(dplyr)
library(tibble)

```

```{r}
getwd()
#gettting data from local file
data1 = read_excel("2022CCSurvey_1.xlsx") %>% 
  clean_names() 

```

# 1. What Chippewa County township(s) do you farm in?
```{r}
#Chippewa County Township Shapefile
Chip_shp= st_read("Towns")
```

```{r}
#filtering data to townships and then counting # of responses for each township
townships <- data1 %>% 
  select(township) %>%
  separate_rows(township, sep = ",") %>%
  count(township, sort = TRUE) %>%
  rename(farmers = n)
```

```{r}
#Joining township counts to shapefile information including areas with no response
Chip_shp = Chip_shp %>%
  left_join(townships, by = c("NAME" = "township")) %>%
  mutate(farmers = ifelse(is.na(farmers), 0, farmers))
```

```{r, fig.height = 8, fig.width = 12}
#plotting the map with scale fill based on # of responses for each township
Q1_plot = ggplot(Chip_shp, aes(fill = farmers)) +
  geom_sf() +
  scale_fill_gradient2(midpoint = 3.5, mid = "green3", low = "white", high = "green4") +
  #annotate(geom = "text", ) +
  geom_sf_label(aes(label = NAME), size = 4) +
  theme(plot.title = element_text(size = 20),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 14)) +
  labs(title = "Farmer Use of 2022 Cost-Share for Chippewa County WI Townships")

Q1_plot
```

```{r}
ggsave("CCTownships_2022.png", plot = Q1_plot, height = 8, width = 12, dpi = 300)
```


# 2. Total number of 2022 cropland acres & 3. Total number of 2022 fall cover crops planted
```{r}
Q2 = data1 %>%
  select(respondent,acres_crop,acres_cc) %>%
  mutate(percentCC = acres_cc/acres_crop) %>%
  rename(acres.1= acres_crop, acres.2= acres_cc)%>%
  filter(!is.na(acres.1))
```

```{r}
Q2.1 = Q2 %>%
  pivot_longer(cols= c("acres.1","acres.2"),
               names_to = 'acres',
               values_to = 'response') %>%
  mutate(acres = fct_recode(acres,
                               "cover crop" = "acres.2",
                               "total crop" = "acres.1"),
         percentCC = round(percentCC*100,0))

Q2.2 = Q2.1 %>%
  group_by(respondent) %>%
  mutate(percentCC = na_if(percentCC, lag(percentCC))) %>%
  ungroup()
```


```{r, fig.width = 7, fig.height = 7}
#Total Cropland acres and cover crop acres in 1 plot with percentage to the right
Q2_plot = Q2.2 %>%
  mutate(respondent = as.factor(respondent),
         respondent = fct_reorder(respondent, response)) %>%
  ggplot(aes(x= respondent, y= response, fill= acres)) +
  geom_col(position = "identity") +
  scale_fill_manual(values = c("gold3","green4")) +
  geom_text(aes(label = percentCC), nudge_y = 110, size = 4) +
  labs(title = "Cover Crop, Cropland, & % Cover Cropped Acres", y = "acres", x = "Chippewa County farms") +
  theme(panel.background = element_rect(fill = 'gray80'),
        plot.title = element_text(size = 20),
        axis.title.x = element_text(size = 15),
       axis.title.y = element_text(size = 15),
       axis.text.x = element_text(size = 15),
       axis.text.y = element_blank(),
       axis.ticks.y = element_blank()) +
  coord_flip()

Q2_plot
#ignore error message, the values are intended to be missing.
```

```{r}
ggsave("Crop_CCAcreage_2022.png", plot = Q2_plot, height = 7, width = 7, dpi = 300)
```


# 4. Previous crops
```{r}
Q4 = data1 %>%
  separate_rows(prior_crops, sep = ",") %>%
  count(prior_crops, sort= TRUE) %>%
  rename(response = prior_crops) 

#trying to get a count on the number of responses for a certain variable
Q4_n = data1 %>%
  select(respondent, prior_crops) %>%
  filter(!is.na(prior_crops)) 

#count(Q4_n,respondents)
 
```

```{r, fig.height = 5, fig.width = 7}
Q4_plot = Q4 %>%
  ggplot(aes(x = response, y = n)) +
  geom_col(fill = "gold3") +
  geom_text(aes(label= n), nudge_y= 1, size = 5) +
  theme(panel.background = element_rect(fill = 'gray80'),
        legend.position = "none",
        axis.title.x = element_text(size = 15),
        axis.title.y = element_blank(),
        axis.text = element_text(size = 15),
        plot.title = element_text(size = 20)) +
  scale_y_continuous(limits= c(0,30), breaks = c(0,5,10,15,20,25)) +
  labs(title= "Previous Crop(s)", y = "# of responses") + #look at using caption to add sample size
  coord_flip()

Q4_plot
```

```{r}
ggsave("PreviousCrop_2022.png", plot = Q4_plot, height = 5, width = 7, dpi = 300)
```

# 5. 20222 cover crop planting date range
```{r}
planting_date1 = data1 %>%
  select(respondent, firstplant_date, dec_height) %>%
  mutate(plant_date = as.Date(firstplant_date)) %>%
  select(respondent, plant_date, dec_height)

planting_date2 = data1 %>%
  select(respondent, lastplant_date, dec_height) %>%
  mutate(plant_date = as.Date(lastplant_date)) %>%
  select(respondent, plant_date, dec_height)

planting_date = rbind(planting_date1,planting_date2) %>%
  filter(!is.na(plant_date)) %>%
  rename(Height = dec_height)

```

```{r, fig.width = 7, fig.height = 5}
 Q5_plot = planting_date %>%
  ggplot(aes(x = plant_date, y = respondent, group = respondent, color= Height)) +
  geom_point(size = 3) +
  geom_line(linewidth = 2) +
  scale_color_gradient2(midpoint = 6, mid = "yellow", low = "red", high = "green4") +
  scale_x_date(limit= c(as.Date("2022-08-01"), as.Date("2022-12-01"))) +
  ylim(0,36) +
  theme(panel.background = element_rect(fill = 'gray80'),
        plot.title = element_text(size = 20),
        axis.title.x = element_blank(),
       axis.title.y = element_blank(),
       axis.text.x = element_text(size = 15),
       axis.text.y = element_blank(),
       axis.ticks.y = element_blank()) +
  labs(title = "2022 Cover Crop Planting Dates")

Q5_plot
```

```{r}
ggsave("CCPlantingDate_2022.png", plot = Q5_plot, height = 5, width = 7, dpi = 300)
```


# 6. What Species did you plant
```{r}
Q6= data1 %>%
  separate_rows(cc_species, sep = ",") %>%
  count(cc_species, sort = TRUE) %>%
  rename(response = cc_species)
```

```{r, fig.width = 7, fig.height = 5}
Q6_plot = Q6 %>%
  ggplot(aes(x = response, y = n)) +
  geom_col(fill = "green4") +
  geom_text(aes(label= n), nudge_y= 1.25, size = 5) +
  theme(panel.background = element_rect(fill = 'gray80'),
        legend.position = "none",
        axis.title.x = element_text(size = 15),
        axis.title.y = element_blank(),
        axis.text = element_text(size = 15),
        plot.title = element_text(size = 20)) +
  scale_y_continuous(limits= c(0,37), breaks = c(0,5,10,15,20,25,30,35)) +
  labs(title= "Cover Crop Species", y = "# of responses") +
  coord_flip()

Q6_plot
```

```{r}
ggsave("CCSpecies_2022.png", plot = Q6_plot, height = 5, width = 7, dpi = 300)
```

# 7. Seeding rate(s)
```{r}
Q7= data1 %>%
  select(respondent,cc_rate,cc_type) %>%
  separate_rows(c(cc_rate,cc_type), sep = ",") %>%
  mutate(cc_rate = as.numeric(cc_rate)) %>%
  rename(response = cc_rate,
         type = cc_type)

```

```{r, fig.width = 4, fig.height = 6}
Q7_plot = Q7 %>%
  ggplot(aes(x= type, y = response, color= type)) +
  geom_jitter(size=3) +
  scale_color_manual(values = c("purple1","green4","red")) +
  theme(panel.background = element_rect(fill = 'gray80'),
        legend.position = "none",
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=15),
        axis.text = element_text(size = 15),
        plot.title = element_text(size = 20)) +
  scale_y_continuous(limits= c(0,310), breaks = c(0,30,60,90,120,150,200,300)) +
  labs(title= "Cover Crop Seed Rate", y = "seeding rate (lbs/acre)") 

Q7_plot
```

```{r}
ggsave("CCSeedRate_2022.png", plot = Q7_plot, height = 6, width = 4, dpi = 300)
```

# 8. Planting method(s)
```{r}
Q8= data1 %>%
  select(respondent,cc_plant) %>%
  separate_rows(cc_plant, sep = ",") %>%
  count(cc_plant, sort = TRUE) %>%
  rename(response = cc_plant) 
```

```{r, fig.height = 5, fig.width = 7}
Q8_plot = Q8 %>%
  ggplot(aes(x = response, y = n)) +
  geom_col(fill = "green4") +
  geom_text(aes(label= n), nudge_y= 0.5, size = 5) +
  theme(panel.background = element_rect(fill = 'gray80'),
        legend.position = "none",
        axis.title.x = element_text(size = 15),
        axis.title.y = element_blank(),
        axis.text = element_text(size = 15),
        plot.title = element_text(size = 20)) +
  scale_y_continuous(limits= c(0,12), breaks = c(0,5,10)) +
  labs(title= "Cover Crop Planting Method", y = "# of responses") +
  coord_flip()

Q8_plot
```

```{r}
ggsave("CCPlantMethod_2022.png", plot = Q8_plot, height = 5, width = 7, dpi = 300)
```

# 9. Tillage
```{r}
Q9= data1 %>%
  select(respondent,tillage) %>%
  separate_rows(tillage, sep = ",") %>%
  count(tillage, sort = TRUE) %>%
  rename(response = tillage) 
```

```{r, fig.height = 5, fig.width = 7}
Q9_plot = Q9 %>%
  ggplot(aes(x = response, y = n)) +
  geom_col(fill = "saddlebrown") +
  geom_text(aes(label= n), nudge_y= 1.25, size = 5) +
  theme(panel.background = element_rect(fill = 'gray80'),
        legend.position = "none",
        axis.title.x = element_text(size = 15),
        axis.title.y = element_blank(),
        axis.text = element_text(size = 15),
        plot.title = element_text(size = 20)) +
  scale_y_continuous(limits= c(0,26), breaks = c(0,5,10,15,20,25)) +
  labs(title= "Tillage", y = "# of responses") +
  coord_flip()

Q9_plot
```

```{r}
ggsave("CCTillage_2022.png", plot = Q9_plot, height = 5, width = 7, dpi = 300)
```

# 10. Manure
## Number of respondents who applied manure
```{r}
Q10= data1 %>%
  select(respondent,manure,manure_rate,manure_source,manure_timing) %>%
  filter(!is.na(manure)) 

```

```{r}
Q10.1 = Q10 %>% #How many farmers applied manure
  count(manure, sort = TRUE)

Q10.2 = Q10 %>% #Liquid manure Rate
  filter(manure == "liquid",
         !is.na(manure_rate)) %>%
  mutate(order = c('D','A','B','C')) #creating random ordered variable to randomize presentation in figure

Q10.3 = Q10 %>% #What was the timing of applied manure
  filter(!is.na(manure_timing)) %>%
  count(manure_timing, sort = TRUE) 
```

```{r, fig.height = 5, fig.width = 7}
Q10.1_plot = Q10.1 %>%
  ggplot(aes(x = manure, y = n)) +
  geom_col(fill = "tan4") +
  geom_text(aes(label= n), nudge_y= 1.25, size = 5) +
  theme(panel.background = element_rect(fill = 'gray80'),
        legend.position = "none",
        axis.title.x = element_text(size = 15),
        axis.title.y = element_blank(),
        axis.text = element_text(size = 15),
        plot.title = element_text(size = 20)) +
  scale_y_continuous(limits= c(0,33), breaks = c(0,5,10,15,20,25,30)) +
  labs(title= "Farmers Applying Manure", y = "# of responses") +
  coord_flip()

Q10.1_plot
```

```{r, fig.height = 1.75, fig.width = 7}
Q10.2_plot = Q10.2 %>%
  ggplot(aes(x= order, y = manure_rate)) +
  geom_point(color = "tan4", size =4) +
  #geom_text(aes(label= n), nudge_y= 1.25, size = 5) +
  theme(panel.background = element_rect(fill = 'gray80'),
        legend.position = "none",
        axis.title.x = element_text(size = 15),
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.ticks.y = element_blank(),
        plot.title = element_text(size = 20)) +
  scale_y_continuous(limits= c(0,7000), breaks = c(0,1000,2000,3000,4000,5000,6000,7000)) +
  labs(title= "Liquid Manure Rates", y = "manure rate (gallons/acre)") +
  coord_flip()

Q10.2_plot
```

```{r, fig.height = 3, fig.width = 7}
Q10.3_plot = Q10.3 %>%
  ggplot(aes(x = manure_timing, y = n)) +
  geom_col(fill = "tan4") +
  geom_text(aes(label= n), nudge_y= 0.25, size = 5) +
  theme(panel.background = element_rect(fill = 'gray80'),
        legend.position = "none",
        axis.title.x = element_text(size = 15),
        axis.title.y = element_blank(),
        axis.text = element_text(size = 15),
        plot.title = element_text(size = 20)) +
  scale_y_continuous(limits= c(0,5), breaks = c(0,1,2,3,4,5)) +
  labs(title= "Application Before or After Cover Crop Planting", y = "# of responses") +
  coord_flip()

Q10.3_plot
```


```{r}
ggsave("ManureApplied_2022.png", plot = Q10.1_plot, height = 5, width = 7, dpi = 300)
ggsave("ManureRate_2022.png", plot = Q10.2_plot, height = 1.75, width = 7, dpi = 300)
ggsave("ManureTiming_2022.png", plot = Q10.3_plot, height = 3, width = 7, dpi = 300)
```


# 11. Seed Source
```{r}
Q11= data1 %>%
  select(respondent,seed,seed_clean,seed_germ) %>%
  separate_rows(c(seed), sep = ",") %>%
  filter(!is.na(seed))
```

```{r}
Q11.1 = Q11 %>%
  count(seed, sort = TRUE) %>%
  rename(response = seed) %>%
  mutate(response = fct_recode(response,
                               'supplier, common variety' = 'common variety',
                               'supplier, improved variety' = 'improved variety',
                               'farmer, bin run' = 'bin run'))

Q11.2 = Q11%>%
  filter(seed == "bin run",
         !is.na(seed_clean)) %>%
  pivot_longer(cols= c("seed_clean","seed_germ"),
               names_to = 'bin_run',
               values_to = 'response') %>%
  mutate(bin_run = fct_recode(bin_run,
                               "clean" = "seed_clean",
                               "germ" = "seed_germ"))

Q11.2_clean = Q11.2 %>%
  filter(bin_run == "clean") %>%
  count(response) %>%
  mutate(bin_run = "seed cleaned")

Q11.2_germ = Q11.2 %>%
  filter(bin_run == "germ") %>%
  count(response) %>%
  mutate(bin_run = "germination tested")

Q11.2 = rbind(Q11.2_clean, Q11.2_germ)
```


```{r, fig.height = 4, fig.width = 7}
Q11.1_plot = Q11.1 %>%
  ggplot(aes(x = response, y = n)) +
  geom_col(fill = "green4") +
  geom_text(aes(label= n), nudge_y= 1.25, size = 5) +
  theme(panel.background = element_rect(fill = 'gray80'),
        legend.position = "none",
        axis.title.x = element_text(size = 15),
        axis.title.y = element_blank(),
        axis.text = element_text(size = 15),
        plot.title = element_text(size = 20)) +
  scale_y_continuous(limits= c(0,28), breaks = c(0,5,10,15,20,25)) +
  labs(title= "Cover Crop Seed Source", y = "# of responses") +
  coord_flip()

Q11.1_plot
```

```{r, fig.height = 7, fig.width = 5}
Q11.2_plot = Q11.2 %>%
  ggplot(aes(x=response, y= n)) +
  geom_col(fill = "green4") +
  geom_text(aes(label= n), nudge_y= 0.5, size = 5) +
  facet_grid(cols=vars(bin_run)) + 
  theme(panel.background = element_rect(fill = 'gray80'),
        legend.position = "none",
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 15),
        axis.text = element_text(size = 15),
        plot.title = element_text(size = 20),
        strip.text.x = element_text(size = 15)) +
  scale_y_continuous(limits= c(0,18), breaks = c(0,5,10,15)) +
  labs(title= "Handling of Bin Run Seed", y = "# of responses")

Q11.2_plot
```


```{r}
ggsave("CCSeedSource_2022.png", plot = Q11.1_plot, height = 4, width = 7, dpi = 300)
ggsave("CCSeedHandling_2022.png", plot = Q11.2_plot, height = 7, width = 5, dpi = 300)
```



# 12. Anticipated use
```{r}
Q12= data1 %>%
  select(respondent,cc_use) %>%
  separate_rows(c(cc_use), sep = ",") %>%
  filter(!is.na(cc_use)) %>%
  count(cc_use, sort = TRUE) %>%
  rename(response = cc_use) 
```

```{r, fig.height = 5, fig.width = 7}
Q12_plot = Q12 %>%
  ggplot(aes(x = response, y = n)) +
  geom_col(fill = "green4") +
  geom_text(aes(label= n), nudge_y= 1.25, size = 5) +
  theme(panel.background = element_rect(fill = 'gray80'),
        legend.position = "none",
        axis.title.x = element_text(size = 15),
        axis.title.y = element_blank(),
        axis.text = element_text(size = 15),
        plot.title = element_text(size = 20)) +
  scale_y_continuous(limits= c(0,33), breaks = c(0,5,10,15,20,25,30)) +
  labs(title= "Intended Cover Crop Use", y = "# of responses") +
  coord_flip()

Q12_plot
```

```{r}
ggsave("IntendedCCUse_2022.png", plot = Q12_plot, height = 5, width = 7, dpi = 300)
```

# 13. Termination method/timing
```{r}
Q13= data1 %>%
  select(respondent,termination) %>%
  separate_rows(c(termination), sep = ",") %>%
  filter(!is.na(termination)) %>%
  count(termination, sort = TRUE) %>%
  rename(response = termination) 
```

```{r, fig.height = 5, fig.width = 7}
Q13_plot = Q13 %>%
  ggplot(aes(x = response, y = n)) +
  geom_col(fill = "green4") +
  geom_text(aes(label= n), nudge_y= 1.25, size = 5) +
  theme(panel.background = element_rect(fill = 'gray80'),
        legend.position = "none",
        axis.title.x = element_text(size = 15),
        axis.title.y = element_blank(),
        axis.text = element_text(size = 15),
        plot.title = element_text(size = 20)) +
  scale_y_continuous(limits= c(0,20), breaks = c(0,5,10,15,20)) +
  labs(title= "Planned Termination Method", y = "# of responses") +
  coord_flip()

Q13_plot
```

```{r}
ggsave("CCTermination_2022.png", plot = Q13_plot, height = 5, width = 7, dpi = 300)
```

# 14. Reason for planting cover crops
```{r}
Q14= data1 %>%
  select(respondent,reason) %>%
  separate_rows(c(reason), sep = ",") %>%
  filter(!is.na(reason)) %>%
  count(reason, sort = TRUE) %>%
  rename(response = reason)
```

```{r, fig.height = 5, fig.width = 7}
Q14_plot = Q14 %>%
  ggplot(aes(x = response, y = n)) +
  geom_col(fill = "green4") +
  geom_text(aes(label= n), nudge_y= 1.25, size = 5) +
  theme(panel.background = element_rect(fill = 'gray80'),
        legend.position = "none",
        axis.title.x = element_text(size = 15),
        axis.title.y = element_blank(),
        axis.text = element_text(size = 15),
        plot.title = element_text(size = 20)) +
  scale_y_continuous(limits= c(0,33), breaks = c(0,5,10,15,20,25,30)) +
  labs(title= "Reason for Planting Cover Crops", y = "# of responses") +
  coord_flip()

Q14_plot
```

```{r}
ggsave("CCReason_2022.png", plot = Q14_plot, height = 5, width = 7, dpi = 300)
```

# 15. Biggest Cover Crop Challenges in 2022
```{r}
Q15= data1 %>%
  select(respondent,challenges) %>%
  separate_rows(c(challenges), sep = ",") %>%
  filter(!is.na(challenges)) %>%
  count(challenges, sort = TRUE) %>%
  rename(response = challenges) #need to clean these up. I don't think these are worth plotting.
```

```{r}
Q15_plot = Q15 %>%
  ggplot(aes(x = response, y = n)) +
  geom_col(fill = "green4") +
  geom_text(aes(label= n), nudge_y= 1.25, size = 5) +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_text(size = 15),
        axis.title.y = element_blank(),
        axis.text = element_text(size = 15),
        plot.title = element_text(size = 20)) +
  scale_y_continuous(limits= c(0,30), breaks = c(0,5,10,15,20,25,30)) +
  labs(title= "Reason for Planting Cover Crops", y = "# of responses") +
  coord_flip()

Q15_plot
```


# 16. Unanswered Questions About Cover Crops
```{r}
Q16= data1 %>%
  select(respondent,unanswered_questions) %>%
  separate_rows(c(unanswered_questions), sep = ",") %>%
  filter(!is.na(unanswered_questions)) %>%
  count(unanswered_questions, sort = TRUE) %>%
  rename(response = unanswered_questions)
```

```{r, fig.height = 5, fig.width = 9}
Q16_plot = Q16 %>%
  ggplot(aes(x = response, y = n)) +
  geom_col(fill = "green4") +
  geom_text(aes(label= n), nudge_y= 1.25, size = 5) +
  theme(panel.background = element_rect(fill = 'gray80'),
        legend.position = "none",
        axis.title.x = element_text(size = 15),
        axis.title.y = element_blank(),
        axis.text = element_text(size = 15),
        plot.title = element_text(size = 20)) +
  scale_y_continuous(limits= c(0,15), breaks = c(0,5,10,15)) +
  labs(title= "Cover Crop Questions", y = "# of responses") +
  coord_flip()

Q16_plot
```

```{r}
ggsave("CCQuestions_2022.png", plot = Q16_plot, height = 5, width = 9, dpi = 300)
```


